Thesis Title

### 2022-03-21 chapters/introduction.tex
fix missing footnotes

As explored in \secref{ssec:reads_2_genomes}, longer sequences are more informative than shorter sequencing data, as the one obtained from second-generation sequencing (see \secref{ssec:2nd_gen_seq}), and can provide a more complete picture of the microbial community in a given samples. 
Several dedicated metagenomic assembly tools are available, such as metaSPAdes\footnote{\url{}}  and MegaHIT\footnote{\url{}} \citep{nurk_metaspades_2017, li_megahit_2015}. 
These tools, in comparison to single-cell data assemblers, are better at dealing with the combination of intra and intergenomic repeats and uneven sequencing coverage \citep{olson_metagenomic_2017}.
For third-generation sequencing, dedicated metagenomic assemblers have recently emerged, such as meta-flye\footnote{\url{https://github.com/fenderglass/Flye/}} which expands on the original flye assembler by overcoming a k-mer selection limitation on low abundance species \citep{kolmogorov_metaflye_2020}. Nevertheless, the use of non dedicated assemblers for metagenomics may come with the cost of wrongly interpret variation as error, especially in samples that contained closely related species and the construction of chimeric sequences as traditional assemblers follow the basic principle that the coverage in a sample is constant \citep{teeling_current_2012}.

>>>>

As explored in \secref{ssec:reads_2_genomes}, longer sequences are more informative than shorter sequencing data, as the one obtained from second-generation sequencing (see \secref{ssec:2nd_gen_seq}), and can provide a more complete picture of the microbial community in a given samples. 
Several dedicated metagenomic assembly tools are available, such as metaSPAdes\footnote{\url{https://github.com/ablab/spades/}}  and MegaHIT\footnote{\url{https://github.com/voutcn/megahit/}} \citep{nurk_metaspades_2017, li_megahit_2015}. 
These tools, in comparison to single-cell data assemblers, are better at dealing with the combination of intra and intergenomic repeats and uneven sequencing coverage \citep{olson_metagenomic_2017}.
For third-generation sequencing, dedicated metagenomic assemblers have recently emerged, such as meta-flye\footnote{\url{https://github.com/fenderglass/Flye/}} which expands on the original flye assembler by overcoming a k-mer selection limitation on low abundance species \citep{kolmogorov_metaflye_2020}. Nevertheless, the use of non dedicated assemblers for metagenomics may come with the cost of wrongly interpret variation as error, especially in samples that contained closely related species and the construction of chimeric sequences as traditional assemblers follow the basic principle that the coverage in a sample is constant \citep{teeling_current_2012}.
